---
title: "lab_12"
author: "derek willis"
date: "2023-05-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## You will need

* tidytext and our usual libraries

## Load libraries and establish settings

**Task** Create a codeblock and load appropriate packages and settings for this lab.
```{r}
library(tidyverse)
library(tidytext)
library(janitor)
library(lubridate)
library(rvest)
```

## Questions

**Q1.** You've been assigned to report a story about the leading reasons that Maryland attorneys get sanctioned by the state for misconduct. The state [publishes lists of sanctions](https://www.courts.state.md.us/attygrievance/sanctions) that contain a short text description about the situation. Load the CSV file in the data folder containing records from fiscal year 2011 onwards. Make a list of unique words from the text column, then following the example in the pre_lab, remove common "stop words" from that list and create a list of the top 10 words containing the percentage of occurrences each word represents. What's the leading word in that answer and, broadly, what do you think the top 10 words describe?

**A1.** Client is the leading word in the answer. I think the top 10 words describe the financial penalties imposed by a judge on a party or attorney for violation of a court rule, according to dictionary.law.com. 

```{r}
md_attorney_sanctions <- read_csv("data/md_attorney_sanctions.csv")

unique_words <- md_attorney_sanctions %>% select(text) %>% 
  unnest_tokens(word, text)


unique_words %>%
  count(word, sort = TRUE) %>%
  top_n(25) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
      labs(x = "Count",
      y = "Unique words",
      title = "Count of unique words found in Maryland Attorney Sanctions and Actions")

data("stop_words")

stop_words <- stop_words %>% 
  add_row(word = 'disbared') %>%
  add_row(word = 'failing') %>%
  add_row(word = 'respondent') %>% 
  add_row(word = 'consent') %>% 
  add_row(word = 'reciprocal') %>% 
  add_row(word = 'arizona') %>%
  add_row(word = 'safekeep') %>%
  add_row(word = 'attorney') %>%
  add_row(word = 'engaging') %>% 
  add_row(word = 'dishonesty') %>% 
  add_row(word = 'misrepresentation') %>% 
  add_row(word = 'trademark') %>% 
  add_row(word = 'abandoned') %>% 
  add_row(word = 'abandonments')

unique_words %>%
  anti_join(stop_words) %>%
  group_by(word) %>%
  tally(sort=TRUE) %>%
  mutate(percent = (n/sum(n))*100) %>%
  top_n(10)
```

**Q2.** Let's move beyond single words to phrases. Make a list of the top 10 three-word phrases, called trigrams, based on the example from the pre_lab (you'll need to modify the example code to do this). What's the top trigram and how often does it appear? What does that phrase mean in legal terms?

**A2.** The top trigram is 'adequately communicate with' and it appears 153 times throughout all the texts. This means that your supervisor is informed about where you are, what the state of the art of your work is during the research process, if you are facing delays, difficulties, uncertanties and tthe like, according to lawinsider.com.

```{r}
md_attorney_sanctions %>% 
  filter(fiscal_year >= '2011', fiscal_year < '2023') %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3) %>%
  separate(trigram, c("word1", "word2", "word3"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  mutate(trigram = paste(word1, word2, word3, sep=" ")) %>%
  group_by(trigram) %>%
  tally(sort=TRUE) %>%
  mutate(percent = (n/sum(n))*100) %>%
  top_n(10)
```

**Q3.** Let's drop back down to more traditional text analysis - take the top trigram from Q2 and write code to see how many times it occurs in the text column in each fiscal year. What do you think the answer produced by your code suggests? What else could you do to try and clarify the most important reasons attorneys get sanctioned?

**A3.** A sanction is a penalty of varying degrees of severity that provides incentives for obedience to the law, rules and regulations according to Legal Blaze. The top three-word phrases involves the words adequately communicate and dishonesty. Both of these insinuate something negative is happening, so it is safe to say that lawyers in Maryland have been sanctioned because of dishonesty and not adequately communicating. I think the code suggests that there are a lot of sanctions that involve the same things in the years 2011-2023.   

```{r}
md_attorney_sanctions %>%
  filter(fiscal_year >= '2011', fiscal_year < '2023') %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3) %>%
  separate(trigram, c("word1", "word2", "word3"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  mutate(trigram = paste(word1, word2, word3, sep=" ")) %>%
  group_by(trigram) %>%
  tally(sort=TRUE) %>%
  mutate(percent = (n/sum(n))*100) %>%
  top_n(10) %>% 
  count(trigram, sort = TRUE) %>%
  mutate(trigram = reorder(trigram, n)) %>%
  ggplot(aes(x = trigram, y = n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
      labs(x = "Count",
      y = "Unique 3-word phrases",
      title = "Count of unique words found in Maryland Attorney Sanctions and Actions")
```
